% \Chapter{Irodalomjegyzék}
\begin{thebibliography}{9}
\addcontentsline{toc}{chapter}{Irodalomjegyzék}
% \addcontentsline{toc}{chapter}{Irodalomjegyzék}

% http://books.google.de/books?hl=de&lr=&id=nEh4D4e88NwC&oi=fnd&pg=PA1&dq=Formal+Concept+Analysis+Fondations+and+Applications&ots=GSCkikE8pv&sig=8TJOPrSW07sJqLH0hF8_-HH_gb4#v=onepage&q=Formal%20Concept%20Analysis%20Fondations%20and%20Applications&f=false

% http://www.google.com/books?id=nEh4D4e88NwC&lpg=PA1&ots=GSFpjeHaqq&dq=bernhard%20ganter%20rudolf%20wille%20formal%20concept%20analysis%202004&lr&hl=hu&pg=PA2#v=onepage&q=bernhard%20ganter%20rudolf%20wille%20formal%20concept%20analysis%202004&f=false

\bibitem[AS09]{AS09}
Andrews, S.: \emph{In-Close, a fast algorithm for computing formal concepts},\\
International Conference on Conceptual Structures (ICCS),\\
Moscow, 2009.

\bibitem[KC10]{KC10}
Kristina Chodorow, Michael Dirolf: \emph{MongoDB: The Definitive Guide}, \\
O'Reilly Media, 2012.

\bibitem[GW05]{GW05}
Bernhard Ganter, Gerd Stumme, Rudolf Wille:\\
\emph{Formal Concept Analysis, Foundations and Applications},\\
Springer, 2005.

% http://link.springer.com/chapter/10.1007%2F978-3-540-78582-8_9#page-1
% http://www.palgrave-journals.com/kmrp/journal/v8/n3/full/kmrp201010a.html
\bibitem[KB08]{KB08}
Hak-Lae Kim, John G. Breslin, Sung-Kwon Yang, Hong-Gee Kim: \\
\emph{Social Semantic Cloud of Tag: Semantic Model for Social Tagging} \\
Springer-Verlag Berlin Heidelberg, 2008.

\bibitem[KL07]{KL07}
Kovács László: \emph{Generating Decision Tree from Lattice for Classification}, \\
Proceeding of ICAI07, Eger, 2007, 377-385.

\bibitem[KA08]{KA08}
Körei Attila: \textit{Fogalomhálók alkalmazása osztályfelbontási problémákra}, \\
PhD értekezés, Miskolci Egyetem, 2008.

% http://dl.acm.org/citation.cfm?id=321481
\bibitem[DM68]{DM68}
Donald R. Morrison: \\
\textit{PATRICIA - Practical Algorithm To Retrieve Information Coded in Alphanumeric}, \\
Journal of the ACM, Volume 15 Issue 4, Oct. 1968.

\bibitem[PP08]{PP08}
Alexandre Passant, Philippe Laublet: \emph{Meaning Of A Tag: A Collaborative Approach to Bridge the Gap Between Tagging and Linked Data} \\
Université Paris-Sorbonne, 2008.

\bibitem[RS98]{RS98}
Radeleczki, S.: \emph{A fogalomhálók egy műszaki alkalmazása}, \\
International Conference on Computer Science, "MicroCAD'98", \\
Section Applied Mathematics, University of Miskolc, March 12., 1998. pp. 1-7.

\bibitem[RR04]{RR04}
Rusty Russel, Daniel Quinlan, Christopher Yeoh: \\
\emph{Filesystem Hierarchy Standard}, \\
Filesystem Hierarchy Standard Group, 2004.

\bibitem[SF12]{SF12}
Steve Francia: \emph{MongoDB and PHP}, \\
O'Reilly Media, 2012.

\bibitem[SS06]{SS06}
Simon Schenk, Olaf Görlitz, Steffen Staab: \\
\emph{TagFS: Bringing Semantic Metadata to the Filesystem}, \\
Institute for Computer Science, University of Koblenz, 2006.

\newpage

% ================================================
\noindent {\huge \textbf{Internetes hivatkozások}}

\bigskip

\bibitem[BL98]{BL98}
Tim Berners-Lee: \textit{Semantic Web Road map}, \\
\texttt{http://www.w3.org/DesignIssues/Semantic.html} \\
Internet, 2013.

\bibitem[Elyse]{Elyse}
Silkwood Software: \emph{Elyse, freedom from folders}, \\
\texttt{http://silkwoodsoftware.com} \\
Internet, 2013.

\bibitem[Nepomuk]{Nepomuk}
\emph{Networked Environment for Personalized, \\
Ontology-based Management of Unified Knowledge}, \\
\texttt{http://nepomuk.kde.org} \\
Internet, 2013.

\bibitem[Referencer]{Referencer}
Referencer, GNOME Document Organiser \\
\texttt{https://launchpad.net/referencer} \\
Internet, 2013.

\bibitem[SpotLight]{SpotLight}
Apple: \textit{OS X. It's what a Mac a Mac} \\
\texttt{http://www.apple.com/osx/what-is} \\
Internet, 2013.

\bibitem[Tabbles]{Tabbles}
Yellow Blue Soft: \emph{Tabbles, folders evolved}, \\
\texttt{http://tabbles.net} \\
Internet, 2013.

\bibitem[Tag2find]{Tag2find}
\emph{Tag2find, Tag everything on your desktop}, \\
\texttt{http://www.tag2find.com} \\
Internet, 2013.

\bibitem[TaggedFrog]{TaggedFrog}
LunarFrog Software: \emph{TaggedFrog}, \\
\texttt{http://lunarfrog.com/taggedfrog} \\
Internet, 2013.

\bibitem[Tagsistant]{Tagsistant}
Tagsistant, All your files, quickly and easily. \\
\texttt{http://www.tagsistant.net} \\
Internet, 2013.

\bibitem[Tracker]{Tracker}
\texttt{https://live.gnome.org/Tracker} \\
GNOME (Meta) Tracker \\
Internet, 2013.

\bibitem[WinFS]{WinFS}
WinFS Team Blog \\
\texttt{http://blogs.msdn.com/b/winfs} \\
Internet, 2013.

\end{thebibliography}

